Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-10-31 WSSSPE4_report/WSSSPE4_report.tex
fixing case in open research index title; adding best practices section as confirmed by Ray
adding Software Best Practices for Undergraduates section; fixing other best practices section
adding mission info

@@

\begin{itemize}
\item Verifying best practices \& metrics for sustainable software [Ray Idaszak]
\item Software Sustainability Alliance [Neil \& Jean]
\item Scientific Software Prototyping Infrastructure (S2PI) [Santiago Nunez-Corrales] 
\item CodeMeta working group [Alice Allen]
\item White paper on developing sustainable software [Sandra Gesing]
\item Social Science of Scientific Software [Stuart Geiger]
\item Software development best practices [Jonah Miller]
\item Meaningful metrics for sustainable software [Emily Chen]
\item Coordinating access to CI for research software [Mark Abraham]
\item Software engineering processes tailed for research software [Anshu Dubey]
\item Open research index [Dan]
\item Letters of evaluation for computational scientists [Wolfgang Bangerth]
\end{itemize}

\input{wg_open_research_index}

>>>>

\todo{write info about process}

After this process, the final statements about WSSSPE are:

{\bf Mission}
WSSSPE is an international community-driven organization that promotes sustainable research software by addressing challenges related to the full lifecycle of research software through shared learning and community action.

{\bf Vision}
We envision a world where research software is accessible, robust, sustained, and recognized as a scholarly research product critical to the advancement of knowledge, learning, and discovery.

{\bf Focus areas}
WSSSPE promotes sustainable research software by positively impacting:
\begin{itemize}
\item {\bf Principles and Best Practices}. Promoting best practices in sustainable software
\item {\bf Careers}. Developing and supporting career paths in research software development and engineering
\item {\bf Learning}. Engaging in activities to promote peer learning and interaction
\item {\bf Credit}. Ensuring recognition of research software as an intellectual contribution equal to other research products
\end{itemize}

{\bf Definitions}

Sustainable software has the capacity to endure such that it will continue to be available in the future, on new platforms, meeting new needs.

The research software lifecycle includes:
\begin{itemize}
\item acquiring and assembling resources (including funding and people) into teams and communities
\item developing software
\item using software
\item recognizing contributions to and of software
\item maintaining software
\end{itemize}

@@

\begin{itemize}
\item Verifying best practices \& metrics for sustainable research software [Ray Idaszak]
\item Software Sustainability Alliance [Neil \& Jean]
\item Scientific Software Prototyping Infrastructure (S2PI) [Santiago Nunez-Corrales] 
\item CodeMeta working group [Alice Allen]
\item White paper on developing sustainable software [Sandra Gesing]
\item Social Science of Scientific Software [Stuart Geiger]
\item Software Best Practices for Undergraduates [Jonah Miller]
\item Meaningful metrics for sustainable software [Emily Chen]
\item Coordinating access to CI for research software [Mark Abraham]
\item Software engineering processes tailed for research software [Anshu Dubey]
\item Open research index [Dan]
\item Letters of evaluation for computational scientists [Wolfgang Bangerth]
\end{itemize}

\input{wg_best_practices_sustainability}
\input{wg_best_practices_undergrads}
\input{wg_open_research_index}
